---
title: "Project Title"
author: "Your Name"
date: "2025-04-06"
format: html
---

```{r, setup, message=FALSE}

# This setup block loads necessary packages
library(tidyverse)

```

> **NOTE:** Quarto documents are for exploration and testing; for the final deposit, use `.R` scripts. There should be **ONE** `main.R` script that calls all subsequent `.R` scripts.

# Introduction

Provide a brief introduction to your analysis or research question. Explain what you will explore in this document, including the data and methods used.

For example:

- What is the main question or hypothesis you're testing?
- Why is this research important?
- What datasets are being used?

# Load Data

First, we load the required libraries and data.

```{r}

# Load the data
data <- read.csv("../data/raw/your_data.csv")
head(data)

```

# Data Cleaning and Preprocessing

In this section, we'll clean and preprocess the data to prepare it for analysis.

```{r}

# Clean the data: removing missing values, renaming columns, etc.
data_clean <- data %>%
  filter(!is.na(variable)) %>%
  rename(new_variable = old_variable)

# Check cleaned data
head(data_clean)

```

# Exploratory Data Analysis (EDA)

Here, we explore the dataset by visualizing and summarizing key patterns.

## Summary Statistics

```{r}

# Summary statistics
summary(data_clean)

```

## Visualizing the Data

```{r}

# Visualize the distribution of a variable
ggplot(data_clean, aes(x = new_variable)) +
  geom_histogram(binwidth = 1) +
  labs(title = "Distribution of New Variable")

```

# Model Prototyping

In this section, we'll build a simple model to test our hypothesis.

```{r}

# Example: Linear regression model
model <- lm(dependent_variable ~ independent_variable, data = data_clean)

# View model summary
summary(model)

```

# Results

Here, summarize the results of your analysis or modeling.

For example:

- What did the exploratory data analysis show?
- What insights were gained from the model?

# Conclusion

Wrap up the analysis, summarize key findings, and outline any next steps.

- Discuss whether your hypothesis was supported or rejected.
- What are the implications of the results?
- Are there any limitations to your analysis?

